Prediction of 90-day mortality after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden, England and Wales

### 2020-08-24 reports/article.Rmd
Fix #50

>>>>

~~It should be noted that short-term mortality after elective THA is rare. As such, it might not be the most immediate issue for patients making an informed decision on whether to operate or not. Other pertinent outcomes includes adverse events after surgery such as prosthetic joint infections or dislocation. Our next step is therefore to extend the web calculator to such events as well.~~
